### 2018-07-02 Docs/managing_jobs/managingjobs.tex
amrex -> FBoxLib

All plotfile directories have a {\tt job\_info} file which lists as
host of parameters about the simulation, including:
\begin{itemize}
\item A descriptive name for the simulation (the {\tt job\_name} runtime
  parameter
\item The number of MPI tasks and OpenMP threads
\item The total amount of CPU-hours used up to this point
\item The data and time of the plotfile creation and the directory it was written to.
\item The build date, machine, and directory
\item The \maestro, \boxlib, and other relevant git hashes for the source
\item The directories used in the build
\item The compilers used and compilation flags
\item The number of levels and boxes for the grid
\item The properties of the species carried
\item The tolerances for the MG solves
\item Any warnings from the initialization procedure (note: these are not currently stored on restart).
\item The value of all runtime parameters (even those that were not explicitly set in the inputs file), along with an indicator showing if the default value
was overridden.
\end{itemize}
This file makes it easy to understand how to recreate the run that
produced the plotfile.

@@

\item {\em gfortran 6.1.1}: These compilers have a bug in producing
  optimized code for \boxlib's {\tt init\_layout\_tilearray}.  At the
  moment, this is worked around in \boxlib\ by changing the routine
  from a function to a subroutine.

@@

The \boxlib\ floating point exception trapping is disabled with PGI
compilers earlier than version 16, due to problems with PGI using the
system header files.  From version 16 onward, things should work.

@@

Additionally, if the {\tt ftime} executable is in your path ({\tt
ftime.f90} lives in {\tt BoxLib/Tools/Postprocessing/F\_src/}), then
the script will create a file called {\tt ftime.out} that lists the
name of the plotfile and the corresponding simulation time.

@@

One way to achieve this in \maestro\ is to modify the appropriate make file.  For
PGI, this would be {\tt \$BOXLIB\_HOME/Tools/F\_mk/comps/Linux\_pgi.mak}.  If
this proves useful, it may be worth it to build {\tt Score-P} into the build
infrastructure.

@@

\item Intel 16.0.0 and 16.0.1 have issues compiling the linear solvers
  in \boxlib\ and should be avoided.

  Intel 16.0.2 works fine.

>>>>

All plotfile directories have a {\tt job\_info} file which lists as
host of parameters about the simulation, including:
\begin{itemize}
\item A descriptive name for the simulation (the {\tt job\_name} runtime
  parameter
\item The number of MPI tasks and OpenMP threads
\item The total amount of CPU-hours used up to this point
\item The data and time of the plotfile creation and the directory it was written to.
\item The build date, machine, and directory
\item The \maestro, \fboxlib, and other relevant git hashes for the source
\item The directories used in the build
\item The compilers used and compilation flags
\item The number of levels and boxes for the grid
\item The properties of the species carried
\item The tolerances for the MG solves
\item Any warnings from the initialization procedure (note: these are not currently stored on restart).
\item The value of all runtime parameters (even those that were not explicitly set in the inputs file), along with an indicator showing if the default value
was overridden.
\end{itemize}
This file makes it easy to understand how to recreate the run that
produced the plotfile.

@@

@@

The \fboxlib\ floating point exception trapping is disabled with PGI
compilers earlier than version 16, due to problems with PGI using the
system header files.  From version 16 onward, things should work.

@@

Additionally, if the {\tt ftime} executable is in your path ({\tt
ftime.f90} lives in {\tt amrex/Tools/Postprocessing/F\_src/}), then
the script will create a file called {\tt ftime.out} that lists the
name of the plotfile and the corresponding simulation time.

@@

One way to achieve this in \maestro\ is to modify the appropriate make file.  For
PGI, this would be {\tt \$FBOXLIB\_HOME/Tools/F\_mk/comps/Linux\_pgi.mak}.  If
this proves useful, it may be worth it to build {\tt Score-P} into the build
infrastructure.

@@

\item Intel 16.0.2 works fine.

### 2018-07-02 Docs/preface/preface.tex
amrex -> FBoxLib

\noindent \maestro\ uses the \boxlib\ library,
developed at the Center for Computational Sciences and Engineering at
Lawrence Berkeley National Laboratory.  \boxlib\ is distributed
separately from \maestro\ (see
\url{https://ccse.lbl.gov/BoxLib/})
\\

\noindent The {\tt helmeos} equation of state was developed by Frank Timmes (ASU).
The version in \maestro\ was downloaded from his website and the
interface changes slightly for threadsafeness.  We thank Frank for
making it available.

>>>>

\noindent \maestro\ uses the \fboxlib\ library (and formerly, the
\boxlib\ library), developed at the Center for Computational Sciences
and Engineering at Lawrence Berkeley National Laboratory.  \fboxlib\ is
distributed separately from \maestro\ (see
\url{https://github.com/AMReX-Codes/}) \\
